\documentclass[letterpaper,12pt]{report}

\usepackage[margin=1in]{geometry}

\begin{document}

%Lay-out functions
\def\columns#1#2{
\begin{minipage}[t]{.5\textwidth}
\raggedright
#1
\end{minipage}
\hfill
\begin{minipage}[t]{.5\textwidth}
\raggedright
#2
\end{minipage}
}

\def\act{~\\\line(1, 0){250}~\\}

\def\empty{\vspace{.3cm}\\}

\def\nonopenquotation{}

``Could you pass me the salt please?'' Sofie asked.

It was morning. Sofie and Rob had just woken up and were eating breakfast, meaning it was actually closer to noon, but that's not important. The sun was shining, the birds were singing, Pandin was herding the chickens. Everything was normal.

Rob handed the salt to Sofie. ``Is the egg to your liking? I'm still figuring out how long to cook it for you.''

``Yeah, I think you nailed the timing,'' She took another bite. ``but does your egg have a weird aftertaste as well?''

``I know right.'' He looked at his own egg. ``I think it's-''

The conversation was interrupted by a combination of angry cawing and human cries for mercy.

Rob looked in the direction of the noise. ``Pandin's caught something, someone. Could you give me the binoculars please? They should be below you.''

Sofie reached under her seat and pulled out the binoculars. ``Jos\'ephine's?''

``Could be, but we're not in any of their common patrolling areas.'' Rob took the binoculars and looked through them at the fight. ``False alarm. It's just the `god sent us' folks.'' He put the binoculars back down, before shouting ``\textit{Hey, Pandin! Fangen, nicht T\"oten.}'' He then handed the binoculars back to Sofie, who put them back in their place.

``You just told him to catch him instead of killing him, right? Catching is `\textit{vangen}' in dutch, is it-''

```\textit{Fangen}' in german, yes. Anyway, I think the taste is from the fish. The chickens did have that large portion of spoilt eal two days ago, remember? Should still be edible though. Too bad about the tast-''

The conversation was again interrupted, this time by a woman's shouts: ``\textit{Pandino, for! Perkele! Ne mangxu lin! Li estas amiko, almenaux nune.}'' Sofie didn't recognise the language, but it sounded as if someone was rapidly speaking spanish with a strong slavic accent.

Rob turned towards the voice. ``That's not the `god sent us' people. \textit{Pandin! Ab!}''

Pandin had by this point wrestled his opponent into lying face-down on the ground and was sitting on his head, picking at it whenever he tried to get up or move his head. However after hearing Rob, she reluctantly jumped off. The woman came closer and helped her apparent friend up.

Rob shouted over at her. ``\textit{Simino! Oni ne diris al mi ke vi igxis religiema!}''

``\textit{Mi ne. Cxi tiuj kretenoj `gardas' min kontraux la demono kiun mi volas viziti laux ili.}''

``\textit{Cxu mi? Demono? Ha! Sed venu, venu.}''

Sofie didn't understand a word, but Rob had apparently invited them to come closer since the woman did so, followed by Pandin, Pandin's victim and four more members of the priesthood who came from out of the forest. The woman -Simino, if Sofie hadn't misheard- came all the way to the shore, about two meters from the boat. The priesthood soldiers keps a safe distance. They wouldn't even look at the boat. Instead, they preferred to stare at the ground, hands on their rifles.

Now that the woman had come closer, Sofie could make out what she looked like. She was a bit shorter than the male soldiers accompanying her, and like them wore what appeared to be a military uniform: camo vest and pants, black boots and gloves. Hers was of a different make than theirs however. Her light blonde hair was tied up in a ponytail. On her back she wore a small rucksack and a large rifle. Clothing- and posturewise she actually reminded Sofie a lot of Johan, but she looked quite a bit happier than him.

Rob began talking again, but was interrupted by one of the soldiers. ``Could we speak english please? The rest of us might want to understand what's going on as well.'' He had not looked up while speaking.

Rob gave Simino a questioning look. She replied, ``\textit{Ni faru kion vi preferas. Mia angla ne estas tiel bona, vi ja scias, sed mi travivos gxin.}''

``\textit{Ne, ne. Eble ja estas bona ideo. Sofio ankaux ne scipovas esperanton.}'' With that, he turned to Sofie. ``Sofie, this is Simone. Where she lives they call her Simino.''

Simone looked over at her and smiled. ``\textit{Saluton, Sofio.}''

``Hello.''

``So what brings you and this club of the mentally less than gifted here?'' Rob asked.

Several of the soldiers indicated that they took offense, but did not move.

Simone smiled at their reactions and began speaking again. The fluid and rapid speach she'd had before was gone, replaced by english with a strong, but certainly not slavic, accent. ``I came here to ask for your help. As I told you already, these morons'' -several of them again indicated offense- ``insisted I need protection from the `demon' I'm visiting.''

``So what do you need my help with?''

``We've found the Taker's hiding place.''

``I'm in.''

Rob dropped his spoon, ran inside, and frantically began packing his bag.

``Rob, what's going on?'' Sofie asked, confused.

``Pack your bag, Sofie. We's going on a little trip - Ok I don't actually know if it's little.'' He stuck his head outside. ``Simone, How far is it till there?''

``About two hours on foot.''

He disappeared back inside. ``We're going on a two hour walk. Pack your stuff.'' He threw her bag outside, then ran after it and took it back in. ``No, I'll do it for you, you clear the table.''

``Where are we going?''

``I'll explain on the way there.''

``Can I at least finish my egg?''

``Sure, on the way there.''
\act

Sofie finishes her egg, threw the shell into the bushes next to the road and put away her spoon. ``So where are we going?''

Rob finished adjusting the straps on his backpack and started explaining: ``During the clusterfuck around here five years ago, when a new army marched through every week, there was, as you'd imagine, a lot of crime. Most of it was starving people stealing food, but there were graver things as well. Amongst others, a lot of people went missing.

\nonopenquotation
The majority were resolved after the status quo set in: We found the bodies of those who got shot, and shot those who joined the armies. However, there was one group of disappearances that nobody could explain. Over a vast area, all the way from the Ostsee to where France used to be, and from all sides, young women had gone missing, gone missing from shelters, from camps, from cities, even the military had cases. The first few rounds of negotiotions actually failed because of them. Everybody thought the other side had their girls.

\nonopenquotation
We eventually concluded that these disappearences -which by the way were still going on- weren't tied to any group. As unlikely as it seems, they had to be the work of an individual. So, being their creative selves, people started calling this person `the Taker'. I'm actually surprised the priesthood managed to keep this from you. There was a real wave of `Taker panic' going around.''

``So what happened?'' Sofie asked.

``Well, the disappearances just kinda stopped after a while and most people intentionally forgot the whole thing ever happened. It's frankly amazing someone was still looking.'' He ran forward a bit, to where Simone was. The priesthood soldiers made sure their distance to him remained the same. ``Simone! You said `\textit{We} found the Taker's hiding place'. Who is `we'?''

``Some of Jos\'ephine's people if I'm not mistaken.''

Rob groaned.

``What?'', asked Sofie, who had caught up to them by now.

``It's a publicity stunt. She's trying to make herself seem like a benevolent ruler only out for the good of all.''

``She's not?'', one of the priesthood guards asked. He focused back on the ground in front of him when Rob looked over.

``She's just as self-interested as the rest of you. She's just better at hiding it.''

``Of course, but good deeds are good deeds. The intention doesn't matter.'' Simone said.

``Sure, but she's building up power in the process and I don't like it. Mark my words: This whole situation is going to end in blood eventually.''
\act

They eventually arrived at the `base of operations', a tent somewhere in an opening in the forest. Around it, smaller tents of varying sizes were scattered about. There were also \textit{a lot} of people. Sofie recognized more members of the brotherhood and plenty of soldiers from Jos\'ephines army. Several people dressed in civilian clothes came over to Simone and started talking to her in her language. There were also some groups whom Sofie didn't recognize.

In the center of all this activity stood Fathiyya, Jos\'ephines general. Her head scarf made her stick out quite noticably. She stood at a large table under the tent, apparently organising the operation. Spread on the table were various papers and a large map.

Rob and Simone went over to her. The brotherhood members did not.

``So we meet again,'' Rob said, ``Luckily it is under better circumstances.''

Fatiyya gave some quick instructions to an aide and came over to them. She smiled and shook Rob's hands. ``I would not call it \textit{better} circumstances.''

``Well you're not pointing guns at each other.'' Sofie said.

Fatiyya looked over at Sofie and smiled. ``I recall we were mostly pointing soldiers at each other, but it is nicer this way, yes.'' She shook Sofie's hand as well. Simone and she had apparently already been introduced.

``Jos\'ephine is busy somewhere else I presume? I don't see her around.'' Rob said.

``Jos\'ephine is always busy.''

``Yes, no doubt planning how to cause my next headache, but we'll worry about that when it happens. What's the situation here and now?''

Fatiyya turned back towards the table. ``We managed to trace `the Taker' to this location.'' She pointed it out on the map ``It's an old monastery, used to be a hotel before things turned to shit.''

``How exactly did you trace the Taker?'' Rob asked.

Fatiyya smiled. ``That, I'm afraid, is a trade secret, but before you worry we're exploiting these good people for our own personal gain, here.'' She pulled a bracelet out of her pocket. It had the name `Sophia' inscribed on it.

``The parents confirm that it belongs to their daughter. They were one of ours.'' Simone said.

``Are they okay?'' Sofie asked.

``Yes, yes. They're here in fact. They're hoping to finally get some closure.''

Fatiyya pulled a transparent plastic sheet with markings on it from under the table and carefully laid it over the table. The markings turned out to be an attack plan. ``We've got the building completely surrounded, nothing in or out without my men noticing. There are three entrances, so we've got three strike teams. The teams are mixed, but each has more of one group in it than the others: North is mainly my men, East is mostly our pious friends, South West is mostly Simone's folk. We move in two hours, comb through the place, apprehend our `Taker' friend, rescue whoever can be rescued, and go home to our heroes welcome.''

``Or not, depending on how much the universe hates us today.'' Rob went over to inspect the map and studied it for a few moments. ``It seems like a fine plan to me, but what'd you need me for?''

``I didn't call for you. I of course appreciate the help, but I don't \textit{need} you for anything specific. Though I guess you can-''

``\textit{I} went to get him.'' Simone interrupted, ``My men are not soldiers. South West team could use someone who can keep their calm.''

``We'll that's that then.'' Fatiyya said, ``You can join Simone's team.''
\act

``Men, we're getting some more help!'' Simone had brought them to her strike team. As Fatiyya had said, they were mostly people who seemed to have come with Simone. There were a handfull of them standing around, all dressed in civilian clothing and speaking to each other in the same strange language Simone had spoken that morning. Their weapons varied, but they seemed to be quite well armed.

A small distance from them stood four men from Jos\'ephine's army. They initially started talking to Simone in what Sofie recognised as being finnish, but switched to english once they saw Rob and Sofie couldn't understand them. They were quite talkative. Sofie understood this was their first non-training operation, which they seemed to be somewhat excited about. They all wore the standard uniform of Jos\'ephine's army, meaning they were quite a bit better equipped than even Simone herself.

The five brotherhood members that had accompanied Simone to the boat stood some distance from the other two groups. Sofie recognised their faces, but it would not have been necesary. The large white crosses painted on their armour and helmets made it perfectly clear which group they belonged to. They were also very clearly not happy. ``Having to work with regular heathens is bad enough. Now you expect us to fight alongside this demon and an apostate?''

``It's not my fault you people believe in stupid stuff.'' Sofie said.

``The word of God is not stupid. It is absolute truth.''

``Indeed. Too bad what you believe isn't the word of God.''

The one who had shouted at her simply spat on the ground. Before his spit had even reached the ground however, Simone had kicked the legs out from under him. He performed an almost elegant quarter turn around his center of mass, then smacked against the floor. ``You either get along or you're not coming, understood? My team: my rules.''

The others helped their buddy up, who muttered some vague words of consent.

Simone then turned and pointed at Sofie. ``And you make sure not to provoke them.'' she said, ``You can debate the bible all you want after we're done here, but I don't want to see any arguing untill then.''

``She'll behave.'' Rob said. He poked Sofie to get her out of her dear-in-headlights state. ``Won't you?''

Sofie also agreed to get along.

Marone visibly relaxed. ``You guys have all the equipment you need? Weapons? Armor?''

``I have everything I need.'' Rob tapped the shorty on his hip, and his backpack, where he had his kevlar and helmet. ``but I don't have stuff for Sofie yet. Do you have anything lying around?''

``Sure you don't want anything besides that clunky thing?''

``You know I'm more likely to shoot myself anyway.''

``Ok, your choice. We'll see if we can find anything suitable for her.''
\act

As it turned out, Jos\'ephine had foreseen that unequipped civilians would want to join: They had brought along a collection of spare gear. The storehouse/tent was, however, horribly organised. Everything had simply been dumped on the ground, so that Sofie and Marone were now standing knee deep in helmets, boots, ammo clips and other stuff.

Simone held up a kevlar vest. ``This ought to fit you.'' She threw it over. ``Try it on.''

Sofie put it on.

``Yeah, seems to fit.'' Simone said, before suddenly pulling a helmet from behind her and throwing it on a surprised Sofie's head. Sofie fell over, the helmet still her head. ``Good, that fits as well.'' Simone laughed.

``Ow, that hurt.'' Sofie sat up and began trying to get the helmet straps closed, making a point of not even so much as smiling at Simone's prank.

Simone stopped laughing. ``You're sure you want to go in with us?''

``Rob says I can choose, and I want to come.''

``But are you really sure? It's not going to be pretty.''

``What do you mean?''

``Well, you know. At least a dozen girls have been missing for several years. Even if we find them alive, who knows what state they'll be in?''

``God never gives people more than they can bear.''

Simone sat down on the pile around her. ``If you believe that.''

Sofie looked up. ``You don't believe, do you?''

Simone gave a short laugh. ``You won't meet many people who do if you're going to be travelling with Rob, at least not friendlies, and certainly not many who believe \textit{that}.''

``It's true though, isn't it?''

Simone shrugged. ``I don't know. I guess you'll have to see for yourself.''

Sofie wanted to ask more, but Simone didn't look as if she wanted to continue the conversation.
\act

Fatiyya's voice came through the walkie-talkie. ``All trike teams, this is the commander. Are you in position?''

The other teams reported they were ready. Simone signalled they were in position as well.

South West had once been where supplies were delivered. It was a large garage door, big enough to let trucks in. It didn't look as if it had ever been very reliable, and five years of neglect couldn't have done it much good. The mechanism was stuck.

They had initially tried to unjam it, but had finally just cut a man-sized hole into the thin metal. It was this hole that they had now assembled at.

``Ok, all teams, go in three, two, one. Go!''

The brotherhood members were the first to rush in.

``Well they're quite eager.'' Rob said. He held back Sofie. ``We go last. We won't be much good in a firefight anyway.''

They went in last.

By that time, the others had already searched the garage and the kitchen. There was nothing there. As had been planned, they were now waiting for everybody to gather in the hallway behind the kitchen to start checking the hallways beyond that.

``Ok, everybody stay silent.'' Simone ordered. ``Don't bunch up, in case there's traps, but don't stray from the group either. Keep your hands on your weapons and your ears open. Let's go.''

Progress was slow. Before they could walk any amount down the corridor, every room behind every door on the way had to be checked. Often there would be further doors in those rooms and those would need to be checked as well. They meticulously checked the walls and floors as well, in case there were any secret rooms. After half an hour of this, they had barely made it to the door at the end of the hall.

``You know, I kinda figured this would be more exciting.'' Sofie said.

One of the brotherhood members shushed her.

``What?'', she asked.

He shushed her again

``What?'', she asked again, now slightly more annoyed.

``I heard something.''

``Everybody be quiet.'' Simone ordered.

There was indeed a sound coming from the other side of the door. Not voices, but still apparently from humans.

``Ok, Simo, Anna. You stay here to guard our backs. The rest starts moving towards that sound, but slowly.''

They started progressing much faster now, but still at a walking pace. At every corner, Simone would station some men as guards. This way, when they finally reached the room the sound seemed to come from, it was only Sofie, Rob, Simone, one of her men and the four brotherhood member, whom Simone didn't trust as guards.

Simone had put her ear to the door. ``The sound is definitely coming from this room.''

``What is that though?'' Rob asked.

Even this close, the sound was unidentifyable. It wasn't voices, or crying, as one would expect. It sounded a bit like someone breathing through their mouth, but wrong somehow. It wasn't a machine though. It was far too irregular for that.

``More importantly, what is that smell?'' Sofie asked.

``Can't tell. I guess we'll find out soon.'' She pulled her walkie-talkie out of her pocket. ``Central, this is South West strike team. We're investigating a strange sound near the center of the building, possibly the missing girls.''

``Noted, South West.''

``Ok, go!'' Simone said.

One of her men kicked in the door.

On the other side were the missing girls, though one could not possibly have identified them as such. Their arms and legs had been removed. They were hanging from the ceiling on ropes attached to metal rods in the stumps. There were 12 of them, in two rows on either side of the room. Their eyes had been removed, and they had not noticed anyone entering the room; Their hearing had probably been disabled as well.

The floor was covered in an ankle deep layer of piss and shit. The door was apparently insulated to keep most of the smell out, but not that it was open, everyone's nose was filled with the foul stench.

Everyone except for Simone and Rob ran out to puke. Simone slumped agains the wall. ``You know, I was expecting death and rape. That's bad enough, no? Why does it have ot be this?'' She pulled out her walkie-talkie. ``Central this is South West. We've located the missing girls.''

``Noted. What's their status?''

``Well...''

Rob held out his hand. ``Give me your pistol.''

``Sorry, what?'' Simone was confused.

``Your pistol, now.''

Simone had some trouble getting the gun out of its holster -Her hands were shaking.- but she eventually gave it to Rob.

Rob took it. He checked the magazine. ``And another ammo clip.''

Again, it took some fumbling, but she gave him the ammo clip as well.

``What are you going to-''

``South West, come in.''

Simone picked up the walkie-talkie to answer, but her hand slumped down when she noticed what Rob was doing.

He ran to the nearest girl and placed the gun against her forehead. The girl looked up in the direction of the sensation. It was probably the first sign she'd had that there were people in the room. Rob took some time to make sure he'd placed the gun just right. Then he wispered ``Shhh, it'll be over soon.'' and pulled the trigger.

He went to the next nearest girl and did the same thing, then the next girl, and the girl after that, ...

``South West, report! What is the status of the girls?''

Simone had been staring at Rob, her mouth agape. Shaken out of her trance by the command, she closed her mouth and pulled the walkie-talkie up to it.

``Dead. They're dead.''

Sofie came running in and tackled Rob. They both crashed into the wall at the back of the room.

``What are you doing?'' She yelled. ``We're here to save them!''

``That \textit{is} what I'm doing.'' Rob pushed himself off off the wall and rubbed his shoulder. ``Or would you rather they go on like this?'' He pointed at the girls that were still alive. ``This is not a life worth living.''

``That's not your decicion to make.''

``Then whose is it? I can't ask them. I don't think they know tactile sign language.''

``But killing is wrong.''

``No it isn't. Killing is just an action. Whether it's right or wrong depends on the context. The allies killed when fighting against nazi germany, and I'm killing now.'' He shot another one of the girls. ``In both of those cases it's the right thing to do.''
\act

Simone came back into the room. She had been outside discussing the situation with central. The stench hit her like a wall.

Rob was inspecting one of the bodies. Pandin sat on his shoulder.
\empty
\columns{``Ili ecx sendentigxis! Kial? Feke kial?''}
{``Their teeth have been removed! Why? Fucking why?''}
\columns{``Versxajne por ke ili ne povus mordi.''}
{``Probably so they wouldn't be able to bite.''}
\columns{``Jes, sed ki- Ho ne. For! For la penson!''}
{``Yes, but wh- Oh no. Bad thought! Bad! Go away!''}
\empty
Rob grasped his head as if he had a headache. Pandin flew up.
\empty
\columns{``Kio okazis?''}
{``What's the matter?''}
\columns{``Mi jxus komprenis.''}
{``I just understood.''}
\empty
He tightened his grip.
\empty
\columns{``Mi ne volas kompreni.''}
{``I don't want to understand.''}
\empty
After a while, Rob put his hands back down. There was still pain in his expression though. Pandin came back down and tried to comfort him.
\empty
\columns{``Kiel fartas Sofio?''}
{``How's Sofie?''}
\empty
Sofie had ran out after her confrontation with Rob. He hadn't seen her since.
\empty
\columns{``Ekstere, kriante. Sxi ja memoros cxi-tion.''}
{``Outside, crying. She'll remember this for sure.''}
\columns{``Ni cxiuj memoros cxi-tion. Uloj kiuj legas historion pri gxi kiun skribis iu kiu mem nur auxdis pri gxi memoros cxi-tion.''}
{``We're all going to remember this. People who read an account of this written by someone who himself only heard about it are going to remember this.''}
\empty
He slumped agains the wall, then asked:
\empty
\columns{``Cxu iu estas cxe sxi?''}
{``Is someone with her?''}
\columns{``Kelkaj liberejanoj estas cxe sxi.''}
{``Some of my men are with her.''}
\columns{``Nu tio ja bonas.''}
{``That's good at least.''}
\columns{``Ili estas ankaux krianta.''}
{``They are also crying.''}
\begin{center}
``Schei{\ss}e.''
\end{center}
He walked outside.
\act

Sofie had stopped crying in the meantime. Now she was just sitting with her back against the wall and staring ahead of her. Around her people weren't silent. They were crying, or talking, but Sofie didn't really hear any of it. She was just staring, as if she was in her own little bubble of silence, like a pocket universe separate from the rest of world, just for her.

A sound got through. Sofie looked up.

``Huh?''

``I asked if you were ok.''

The outside world flooded back into her senses: Rob, who had asked the question, standing in front of her; the brotherhood members who were standing a safe distance behind him yelling insults; Simone's men sitting and standing all around her. It took a while for her brain to filter all of this information and notice that she'd been asked a question.

``Yeah I'm ok.''

``Simone says you've been crying.''

``I was.''

Rob was standing in front of her, looking down. She sat in front of him, looking up. About a minute passed like this while both of them tried figuring out what to do next. 

Rob eventually sat down in front of her. ``Look, I'm sorry about what happened ok? I'm sorry you had to see this. I'm sorry I yelled at you.''

``No don't be. I chose to come, and I understand where you were coming from. Just, those girls...''

Sofie looked over to the corner where the parents who had come as part of Simone's group were. The mother was trying to comfort her crying husband while not being able to control her own tears.

``Who would do such a thing?'' Sofie asked. ``Do that to another human being?''

``Probably a disturbed person, someone who lacks empathy, who only sees their own benefit.''

``People like that exist?''

``I know someone like that. They're mentally ill. In the past they'd get treatment, but there's not a lot of mental hospitals around anymore.''

``But we're going to find them, right? Make sure they at least don't hurt anyone else?''

``We'll try, yes.''

Sofie pushed herself up. ``Then let's go.'' She ran over to Simone, who had just come out of the room. ``Simone! Gather everyone! We're gonna catch this bastard.''

Rob was still sitting on the ground, looking after Sofie. He sighed, then pushed himself up as well.
\act

Everyone had been gathered into a circle around Simone, who explaining the plan. They didn't look like much of a strike force, more like a bunch of sad humans. The parents who had come with Simone were still wiping their tears. The rest of her men were worriedly looking over at them, not really paying attention to Simone. The priesthood members had stopped yelling at Rob but were still giving him angry looks. Rob was pointedly ignoring them. The talkative men from Jos\'ephine's army were silently staring at their feet. Simone herself was just passing on orders from Fatiyya. She didn't look too enthousiastic about the situation. Only Sofie had fire in her eyes.

``We located the girls. The only thing left now is to find whoever did this.'' Simone said. She pulled a map out of her pocket and held it besides her. ``While we were... standing here, the other two teams have cleared these two areas, almost the entire building. This means if whoever did this is still here, they're going to be in this small area. That's where we're going.''

She folded up the map and looked at the group around her. ``The principle is the same as beforehand. Stay close, but not too close. Be careful. Don't get killed.''

And with that, they moved out.

Again, it was painfully slow. They cleared room after room, door after door, but they never found anything. Periodically, the other teams would report in, and everyone would hold their breath waiting to hear if they'd found the Taker, but every time it was just ``Hallway cleared - nothing found.''

Half an hour passed like this. An hour passed like this. Nothing. The teams moved ever closer to each other, ever closer to the middle of the area Simone had indicated on the map. Still nothing.

After one and a half hours, they rounded a corner and stumbled upon the North strike team.

Simone unclipped her walkie-talkie from her belt and talked into it: ``East, this is South West. We've just found North. Where are you?''

Before she could get a response, someone from North team pointed and said: ``There.''

Everybody looked around. Indeed, East strike team was standing down the hall. They waved and came over.

The three commanders gathered around a map.

``We've searched this area.'' the commander from North said, indicating a portion of the map with his finger. ``Nothing.''

The commander from East did the same thing. ``We've searched this area. Nothing there either.''

``We've searched the rest.'' Simone said. ``Whoever did this can only be in those three rooms.'' Simone put the map down and pointed at the three rooms in the hallway that North had been searching until South West found them.

``Then let's get him.'' the North commander said. He turned to the troops: ``Ok, everybody pay extra attention. The Taker is in one of those three rooms. Everybody pick one of the doors and keep looking at it, even as we're opening the others. I want eyes on every door at all times. No need for this bastard to get the jump on us.''

Everybody gathered into small groups in front of the doors. They had their guns out, finger on the trigger. Their hands were sweaty. They were nervous.

``You and You,'' The North commander pointed at two of his men. ``come with me. We're going to open these doors one at a time, starting from the right.''

They moved to the first door and positioned themselves. Despite the orders, most people looked over.

``Now!''

They kicked in the door. Dust flew up. There was some confusion for a moment as nobody could see what was going on. The dust settled. Nothing.

The North commander and his two men went inside. The group who had been looking at the door they just kicked in inched closer. The others tried their hardest to keep looking at their doors.

Eventually they came out and positioned themselves at the second door. Everybody reshuffled to from two new groups.

``Fifty percent chance now.'' Sofie said. She checked to make sure her gun was loaded.

Rob looked at her, but decided against saying something.

``Now!''

The situation repeated itself. They kicked in the door. Five years worth of dust flew up. Everybody gripped their guns a bit firmer. They went in. They came out. Everybody relaxed a bit again.

``He's got to be behind that door.'' Sofie said. She checker her gun again.

There was now only one big group left. They'd all clumped in front of the last door in a big semicircle. Sofie had picked the spot directly opposite the door, in the middle of the semi-circle.

``Now!''

Again a massive dustcloud formed. Everybody raised their guns in anticipation. Any minute now, the Taker would come running out and they'd gun him down.

Again, the dust settled, and nothing had happened.

The men at the door went in. Nobody dared lower their weapon in case it was just a trick, but when they came back out it was clear: The Taker wasn't here.

There was silence. Nobody knew what to say. People started looking around, seeing who was going to say something. They started lowering their weapons. Still nobody said anything.

``Wh-What happened?'' Sofie said. ``We searched every room, didn't we?''

People started murmuring.

``We did.'' Simone said. ``We checked.''

``Well then check again!''

The murmuring got louder.

``There's not point. I'm telling you we checked everything.''

``But we didn't find him. So what happened?''

Simone was starting to get annoyed. ``I didn't think I'd have to spell this out: He got away.''

Sofie stopped. ``but...''

``What?''

Sofie continued in a very soft tone. ``But it was supposed to be impossible for anyone to leave without being noticed.''

``You'll have to take that up with Fatiyya, because he's not here, is he? What? Do you think he turned to dust? We didn't find him, so he must've gotten away.''

At this point, basically nobody was paying any more attention to Sofie and Simone's discussion. What had started as whispered murmuring was now people shouting at each other. Members of the priesthood were shouting something about this being the hearthen's faulth while another part of their group were chanting psalms to request forgiveness. Simone's men were busy comforting their crying friends. Rob and the other commanders were discussing something over the map.

Sofie sat down and hugged her legs. ``It can't be.''

``Why not.'' Simone was basically yelling now. ``Why. The fuck. Not?''

Sofie couldn't bear to look at Simone anymore. ``God wouldn-''

``What god wouldn't? The spiteful ass those guys worship?'' She pointed at the shouting brotherhood members.

``He's not like that. He loves us. He... He...''

``Say that again? He \textit{loves} us? Did he love those 12 girls Rob had to shoot? Lot of good it did them, right.''

``He does. It's just...''

``It's just what? Fucking what? Cause I don't get you. Twelve girls get mutilated so badly even their parents say Rob did the right thing. That's a tragedy, but things happen, you know? But the guy who did it gets away and little miss zealot doesn't get to fulfill her revenge fantasy, that's impossible? What rock have you been living under for the past five years? Look outside! The world is fucked! Either those freaks over there are right and god is actively hates us, or he has forsaken us! Open your god damned eyes!''

Pandin interrupted Simone by flying into her face, angrily crowing all the while. Simone swatted her away.

``What?'' she yelled.

Pandin ignored Simones. Instead, she flew over to Sofie, who had curled up into a ball and was crying, and started to comfort her.

``Oh.''
\act

Sofie was sitting on a bench outside of the building, wrapped in a blanket -One of Simone's men had given it to her-, staring at her feet. Around her people were wrapping up the operation. Lots of bodies to be disposed of.

``You hungry?''

Sofie looked up. It was Rob. She shook her head and continued to look at, but not see, her feet.

``I see. You want an oat cookie?'' He held one out.

``Thanks, but I'm really not hungry.''

He sat down next to her. ``Day got to you, huh? Simone says she sorry for yelling at you. She didn't mean it. It was just the moment, you know? We were all a bit out of it.''

She sighed. ``It's not because of Simone. Ok, it is, but she shouldn't apologise. She was right.'' She took some time to order her thoughts. ``You know, the priests always taught us God was two things first and foremost: all-powerful and all-loving. Bad things only happened to bad people, and when they did it was His will.'' She smiled at the silliness of the idea. ``There were a loooooot of bad people according to them.''

She paused and stared into the distance a bit. ``I believed that. I really did.'' More silence. Eventually she continued: ``but then I met you and I learned that sometimes, or often, bad things happen to good people too, because maybe they've made enemies while trying to do the right thing, or they're in an unfortunate position, or maybe they're just unlucky, but I figured God still exists. He just isn't all-powerful. Perhaps he's only a bit more powerful than me and you, you know? He still loves all of us unconditionally, but he can't be everywhere at once, you know? He's doing the best he can.''

She stared into the distance for a while. Rob stayed silent. After a while she continued: ``I liked believing that. It was nice. Something bad would happen to people I knew, like when Jos\'ephine cut of the water supply to Johan and Joan's base, and I could almost hear His voice saying `I'm sorry I can't help you right now. I promise I'll try to make it right. There's just so much suffering, so much to be done.' I thought he let slip only the light stuff. `God never gives you more than you can bear' and all that, you know? And that's what happened. Everything always ended alright.'' She looked at her shoes some more.

She turned, and looked at Rob. ``There is no god, is there?'' Rob avoided her gaze. ``Answer me!'' Her voice was shaky, as if it wasn't sure whether to express anger or sadness.

Rob looked back at her. ``I've found no proof for a god, no.''

``Do you believe in one?''

Rob hesitated. He looked uncomfortable.

``No.''

She returned to looking at her feet. ``What they also taught us was that because god loves us, you shouldn't commit suicide. No matter how bad things are currently, god will always make them better in the end'' She smiled. ``or at least, you know, try to.'' Her smile dissappeared. ``If the universe doesn't care about us, then why should I care about being in it?''

This time, Rob sighed. ``Well, the truth is I don't know myself. I guess it differs from person to person. Perhaps sometimes you shouldn't. Like, some people have terminal cancer. Should they continue living a life that's painful to live? I don't know. It's just, for me, god or the universe doesn't really factor into it much of the time. Like, you've played minecraft, right? That game has zero goals, none whatsoever. It just plops you down on some random world, and you figure out what to do. Yet playing minecraft isn't to bad, is it? It's fun. And sure, sometimes I'll get bored of it and then I'll put it down for a while, do something else for a bit. But I always end up coming back to it, cause there's always something new to try, or something old that's still fun.'' He looked around at the busyness around them, at people smiling and helping each other. ``Maybe one day I'll get bored of it for ever. Maybe one day I'll press `Quit' one last time and put it away for good. I don't know that. I just know that day isn't today.''

``But what will you do when it \textit{is} that day? That day when you get bored of it for ever?''

``Don't know. Haven't thought about it. No reason \textit{to} think about it, really. I mean, what if it's tomorrow? What if it's in twenty years? What does it change? Sure, if I find out I'll get hit by a car tomorrow, I could try to do something about it, but what if I find out I'll get cancer tomorrow and die? Best not to know. It'll only ruin the one day you still have, or, for that matter, the twenty years.''

``So that's your answer? Don't think about it?'' She pulled the blanket closer around her. ``I don't think I can. At least it doesn't feel like I can. It feels like-''

``like the thought of death will just be with you from now on forever, no?''

Sofie looked back to Rob, surprised.

``What? I've been there, you know. Wrapped in a hoodie, in a blanket, holding a pillow and still somehow not soft enough, with bad thought running circles in your mind. I know what you feel. It'll go away. Eventually, you'll go to sleep or you'll get up and do something else and you'll stop thinking the bad thoughts for a while, and afterwards they'll be gone.''

Sofie didn't reply.

``Doesn't really help, huh, knowing that?''

``It does, it does. It made me feel a little bit better. It just...''

``doesn't help make the bad thoughts go away?''

``Yeah, cause not really believing you is part of it. Like, what if I wake up tomorrow and they haven't gone away?''

``Hasn't happened to me yet, but I'd probably go see a doctor, get some meds.''

``What if those don't work.''

``Get some others, excercise more, listen to some happy music. You'll find something.''

``And if I don't?''

``The answer is-''

``don't think about it?''

``Yeah.''

They stopped talking for a while, each in their own little bubble of silence despite the noise around them.

``So, now you want an oat cookie?''

``I'd love one.''

``And can I get some of that blanket?''

``Sure.''

\end{document}